Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-22 paper.qmd
Fixed obtaining the axis of Gau cluster data

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.2,
  axis_pos_x = 0.15,
  axis_pos_y = -0.85,
  axis_labels = names(scaled_gau_data),
  threshold = 0.084)

@@

five_gau_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(0.1, 0.38)) +
  ylim(c(-0.9, -0.5)) +
  interior_annotation("a2", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.3,
  axis_pos_x = -0.7,
  axis_pos_y = -0.7,
  axis_labels = names(scaled_gau_data),
  threshold = 0.084)

@@

five_gau_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.75, -0.35)) +
  ylim(c(-0.75, -0.4)) +
  interior_annotation("a3", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.2,
  axis_pos_x = -0.55,
  axis_pos_y = -0.05,
  axis_labels = names(scaled_gau_data),
  threshold = 0.084)

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.2,
  axis_pos_x = -0.37,
  axis_pos_y = 0.22,
  axis_labels = names(scaled_gau_data),
  threshold = 0.084)

>>>>

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.2,
  axis_pos_x = 0.15,
  axis_pos_y = -0.85,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

@@

five_gau_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2),
    label=rownames(axes), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(0.1, 0.38)) +
  ylim(c(-0.9, -0.5)) +
  interior_annotation("a2", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.3,
  axis_pos_x = -0.7,
  axis_pos_y = -0.7,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

@@

five_gau_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2), 
    label=rownames(axes), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.75, -0.35)) +
  ylim(c(-0.75, -0.4)) +
  interior_annotation("a3", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.2,
  axis_pos_x = -0.55,
  axis_pos_y = -0.05,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.2,
  axis_pos_x = -0.37,
  axis_pos_y = 0.22,
  axis_labels = names(scaled_gau_data),
  threshold = 0)
